### 2018-04-04 paper.Rmd
further updates from call

author: 
  - name          : "Alessandro Sanchez*"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "sanchez7@stanford.edu"
  - name          : "Stephan Meylan*"
    affiliation   : "2"
  - name          : "Mika Braginsky"
    affiliation   : "3"
  - name          : "Kyle E. MacDonald"
    affiliation   : "1"
  - name          : "Daniel Yurovsky"
    affiliation   : "4"
  - name          : "Michael C. Frank"
    affiliation   : "1"

@@

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  This work supported by a Jacobs Foundation Fellowship to MCF.

@@

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

@@

\noindent
Another benefit of this workflow is that the instructor could easily reuse it to demonstrate other concepts or questions that come up during the lecture, e.g., order of production for different types of words such as quantifiers vs. number words or function vs. content words. Moreover, future work on childes-db interactive visualization tools could add part of speech tags, phonological information, and n-grams. This would allow instructors to use childes-db to demonstrate concepts such as when children start producing certain phonological patterns (e.g., consonant clusters), the debate about the extent of the noun/verb bias in children's early vocabulary, and the development of particular syntactic constructions.

@@

In the introduction, we outlined the challenge of getting students started with analyzing data from CHILDES. These barriers include learning the details of a special file format (CHAT) and a command-line tool (CLAN) built to specifically for the CHAT format. This workflow can be daunting to navigate for a beginner. Thus, an instructor would have to spend course time teaching students to use CHAT and CLAN, leaving less time for students to try analyses that might increase their interest in child language acquisition. Moreover,  while CLAN provides a useful tool for interactive exploration,  it does not connect to a pipeline of modern natural language processing tools (e.g., models of word embeddings @mikolov2013distributed), making it difficult for students to explore the data using new NLP tools.

@@

# Acknowledgements

Thanks to Brian MacWhinney for advice and guidance, and to Melissa Kline for her work on ClanToR, which formed a starting point for our work. This work supported by a Jacobs Advanced Research Fellowship to MCF.

>>>>

author: 
  - name          : "Alessandro Sanchez*"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, 450 Serra Mall, Stanford, CA 94305"
    email         : "sanchez7@stanford.edu"
  - name          : "Stephan Meylan*"
    affiliation   : "2"
  - name          : "Mika Braginsky"
    affiliation   : "3"
  - name          : "Kyle E. MacDonald"
    affiliation   : "1"
  - name          : "Daniel Yurovsky"
    affiliation   : "4"
  - name          : "Michael C. Frank"
    affiliation   : "1"

@@

author_note: |
  Thanks to Brian MacWhinney for advice and guidance, and to Melissa Kline for her work on ClanToR, which formed a starting point for our work. This work supported by a Jacobs Advanced Research Fellowship to MCF.

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

@@

Another benefit of this workflow is that the instructor could easily reuse it to demonstrate other concepts or questions that come up during the lecture, e.g., order of production for different types of words such as quantifiers vs. number words or function vs. content words. Moreover, future work on childes-db interactive visualization tools could add part of speech tags, phonological information, and n-grams. This would allow instructors to use childes-db to demonstrate concepts such as when children start producing certain phonological patterns (e.g., consonant clusters), the debate about the extent of the noun/verb bias in children's early vocabulary, and the development of particular syntactic constructions.

@@

In the introduction, we outlined the challenge of getting students started with analyzing data from CHILDES. These barriers include learning the details of a special file format (CHAT) and a command-line tool (CLAN) built to specifically for the CHAT format. This workflow can be daunting to navigate for a beginner. Thus, an instructor would have to spend course time teaching students to use CHAT and CLAN, leaving less time for students to try analyses that might increase their interest in child language acquisition. Moreover,  while CLAN provides a useful tool for interactive exploration,  it does not connect to a pipeline of modern natural language processing tools [e.g., models of word embeddings; @mikolov2013distributed], making it difficult for students to explore the data using new NLP tools.

@@
